Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-26 awipev-CO2.Rmd
Added ESSD boxplot figure

sal_mix_bp <- ggplot(filter(d_long, variable=="sal_mix"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Salinity") +
  mytheme_bp()
temp_11m_bp <- ggplot(filter(d_long, variable=="temp_insitu_11m"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Temp. 11 m (°C)") +
  mytheme_bp()
pco2_bp <- ggplot(filter(d_long, variable=="pco2_corr"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  mytheme_bp()
ph_bp <- ggplot(filter(d_long, variable=="pHint_tot_sf"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("p", H[T]))) +
  mytheme_bp()
at_bp <- ggplot(filter(d_long, variable=="at_calc"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
oa_bp <- ggplot(filter(d_long, variable=="oa"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(Omega[a]))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))

g <- cowplot::plot_grid(sal_mix_bp, temp_11m_bp, pco2_bp, ph_bp, at_bp, oa_bp, ncol=2,
               align="v")
g
#g <- arrangeGrob(T1vp, S1vp, AT1vp, CT1vp, pH1vp, pCO21vp, Oa1vp, ncol=1)
#cowplot::
ggsave(file="figures/boxplots.png", g,  width = 18, height = 14, units = "cm")
#g <- cowplot::plot_grid(T1vp, S1vp, AT1vp, CT1vp, pH1vp, pCO21vp, Oa1vp, ncol=2)
#ggsave(file="figures/fig_paper_monthly_means_1m.png", g, width = 18, height = 14, units = "cm")
```

>>>>

sal_mix_bp <- ggplot(filter(d_long, variable=="sal_mix"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Salinity") +
  mytheme_bp()
temp_11m_bp <- ggplot(filter(d_long, variable=="temp_insitu_11m"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Temp. 11 m (°C)") +
  mytheme_bp()
pco2_bp <- ggplot(filter(d_long, variable=="pco2_corr"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  mytheme_bp()
ph_bp <- ggplot(filter(d_long, variable=="pHint_tot_sf"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("p", H[T]))) +
  mytheme_bp()
at_bp <- ggplot(filter(d_long, variable=="at_calc"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
oa_bp <- ggplot(filter(d_long, variable=="oa"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(Omega[a]))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
g <- cowplot::plot_grid(sal_mix_bp, temp_11m_bp, pco2_bp, ph_bp, at_bp, oa_bp, ncol=2,
               align="v")
ggsave(file="figures/boxplots.png", g,  width = 18, height = 14, units = "cm")
```
